\documentclass{article}
\usepackage{amsmath}


\begin{document}
\title{Typesetting Mathematics in \LaTeX}
\author{Nauman \\ recluze@gmail.com}
\maketitle


\section{Introduction} 
\LaTeX\ is extremely powerful when it comes to typesetting mathematics. It's one of the core strengths of this system. 

\section{Displaying Mathematics}
There are two ways of displaying maths. One is \emph{inline} and the other is \emph{display} format -- in which the whole math sits on its own set of lines.


\subsection{Inline Mode}
We are going to insert a mathematics equation inline here using a pair of \$ signs:    . As you can see, the display (such as line spacing) does not get messed up by the mathematics as it does with word processing softwares. 

\subsection{Display Mode}
We can also display equations in their own set of lines. To do this, we can use the equation environment. 

%\begin{equation}\label{eq:emc}
%
%\end{equation}

As you can see, \LaTeX\ inserts the equation number automatically. We can refer to it using the \verb|\ref| command just as we referred to sections, figures and tables. (E.g. Equation~\ref{eq:emc}.) To get rid of the equation number, simply use the \emph{star variant} of the equation environment. (For this, you need the \texttt{amsmath} package.)

%\begin{equation*}
%
%\end{equation*}

Alternatively, we can use the shorthand keys \verb|\[| and \verb|\]|



\section{Mathematical Features}
\LaTeX\ has many builtin features and you can get many more easily. Here, we'll see some of these features: 

Addition, subtraction, multiplication and division: 


Superscripts and subscripts: 



Summation, union, intersection, big-union, integral: 



Fractions, brackets, square root: 


Greek letters: 



Matrices and vectors. For this, you need to include the \texttt{amsmath} package and then use the \texttt{bmatrix} or \texttt{pmatrix} environment: 



Accents: 



See the \texttt{Math} menu in the IDE for other operations. You can refer to ``Short Math Guide for \LaTeX'' for a lot more examples. 

\section{Using Symbols}
You might come across situations where you need to find new symbols. For this, you can refer to the ``The Comprehensive \LaTeX Symbols List''.  





(Optional) Since this is a long command, we might want to create a shortcut using the \verb|\newcommand| command in the preamble. This also allows us to later change the symbol without having to change the equations. 



\end{document}